TBD

### 2021-02-17 outputs/paper/paper.Rmd
Update the parameters for Q8

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = position_dodge(1)) +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "15% or less", "15-30%", "30-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()

>>>>

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = position_dodge(1)) +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()
